A new method to explicitly estimate the shift of optimum along gradients in multispecies studies

### 2023-01-03 redaction/manuscript_cut.Rmd
Edit Benoit's affiliation

$^1$ Laboratoire de Mathématiques et de leurs Applications, Université de Pau et des Pays de l'Adour, E2S UPPA, CNRS, Anglet, France  
$^2$ Department of Mathematics and Statistics, Macquarie University, Sydney, NSW 2109, Australia  
$^3$ ARC Centre of Excellence for Mathematical and Statistical Frontiers, School of Mathematical Science, Queensland University of Technology, Brisbane, QLD 4072, Australia  
$^4$ CEFE, Univ Montpellier, CNRS, EPHE-PSL University, IRD, Univ Paul Valéry Montpellier 3, Montpellier, France  
$^5$ Parc National du Mercantour, Nice, France  
$^6$ Bureau d'études Entomia, Vaumeilh, France

>>>>

$^1$ Laboratoire de Mathématiques et de leurs Applications, Université de Pau et des Pays de l'Adour, E2S UPPA, CNRS, Anglet, France  
$^2$ School of Mathematical and Physical Sciences, Macquarie University, Sydney, NSW92109, Australia 
$^3$ ARC Centre of Excellence for Mathematical and Statistical Frontiers, School of Mathematical Science, Queensland University of Technology, Brisbane, QLD 4072, Australia  
$^4$ CEFE, Univ Montpellier, CNRS, EPHE-PSL University, IRD, Univ Paul Valéry Montpellier 3, Montpellier, France  
$^5$ Parc National du Mercantour, Nice, France  
$^6$ Bureau d'études Entomia, Vaumeilh, France
